---
title: "Lab 10"
author: "Anna Zauner"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
library(usethis)
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```

## beepr::beep()

fun noises

use `beep()` to give self an audio alert

## for loop + beep

```{r, eval=FALSE}
for(i in rev(seq(1:9999))) (
  print(paste(i, "bottles of beer on the wall"))
)

beep(4)
```

## praise is a nice message

```{r}
praise("${EXCLAMATION}!!! This code works ${adverb_manner}!")

praise("Holy ${creating}, Batman - this code works ${ADVERB_MANNER}!")
```

## cowsay::say to have characters say something

```{r}
say("WOWZA!", by = "buffalo")
```

## usethis for everything

Create fun animal with compliment

 usethis::edit_r_profile()
 
 cowsay::say(praise::praise("You are ${ADJECTIVE}"), by = "buffalo", by_color = "green")
 
 R Project first, then git & GitHub repo.
 
 -usethis::use_git()
 -usethis::use_github()
 
 
 ## paletteer: aggregated color palettes
 
 
```{r}
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  slice_min(n=10, min_pressure) %>% 
  ggplot(aes(x = min_pressure, y = name))+
  geom_col(aes(fill = name))+
  scale_fill_paletteer_d("beyonce::X93")
```
## Map of Jornada LTER Vegitation

```{r}
jornada_veg <- read_sf("doc.kml") %>% 
  select(Name) %>% 
  clean_names()

ggplot()+
  geom_sf(data = jornada_veg, aes(fill = name), color = NA)+
  theme_classic()+
  scale_fill_paletteer_d("ggthemes::manyeys")+
  labs(title = "Jornada Basin LTER Vegitation")

ggsave(filename = "my_awesome_jornada_map.png", width = 8, height = 5)
  
```

